Carp\'{e} Data: Supporting Serendipitous Data Integration in Personal Information Management

### 2012-09-19 chi2012.tex
blahdyblah'

\begin{abstract}
While people naturally draw from diverse information sources in the course of routine decision-making, complementary support for managing diverse, heterogeneous data in digital Personal Information Management (PIM) tools remains poor.  In this paper, we present an exploratory initial investigation of ways to support user-driven, ad-hoc data integration in PIM tools, towards opening up for use the emerging ecosystem of structured data now available via APIs and structured data feeds on the Web.  We conducted an exploratory, sequential, mixed-method study, starting with two pre-studies focusing on blah and blah, finding that blah ad blah.  These

designed and evaluated DataPalette.  
% We find that the ``light-touch'' data integration mechanisms introduced allow people to effectively work with and combine information from multiple sources, and more thoroughly justify their choices 
%% exploratory, sequential mixed-method study of 
\end{abstract}

>>>>

\begin{abstract}
While people naturally draw from diverse information sources in the course of routine decision-making, complementary support for managing diverse, heterogeneous data in digital Personal Information Management (PIM) tools remains poor.  In this paper, we present an exploratory initial investigation of ways to support user-driven, ad-hoc data integration in PIM tools, towards opening up for use the emerging ecosystem of structured data now available via APIs and structured data feeds on the Web.  We conducted an exploratory, sequential, mixed-method study, starting with two pre-studies focusing on blah and blah, finding that blahdyblah.  These observations led to the design of DataPalette, an interface for ``light-touch'' data integration that supported simple drag-and-drop and path-selection mechanisms for managing terminological and structurally heterogeneous data items.  Our lab study of DataPalette showed that users understood the interaction mechanisms introduced and the problems they were designed to solve, and that DesignPalette allowed them to make more carefully informed decisions and draw from more data sources while performing multidimensional subjective choice-based tasks.

% We find that the ``light-touch'' data integration mechanisms introduced allow people to effectively work with and combine information from multiple sources, and more thoroughly justify their choices 
%% exploratory, sequential mixed-method study of 
\end{abstract}
